Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-01 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

\begin{thm}[Non-extensible of Gleason's theorem to general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
a Hilbert space $\Hilb$ of dimension $3$, there is a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}

@@

In other words, if the measurement intervals are too imprecise, the
results we get might contradict to each other, and exclude the possibility
that any state is consistent with the measurement results. Although
we will not dig into the general framework to avoid this problem here~\citep{HOSTunpublished},
we will solve this problem with a concrete family of intervals and
QIVPMs. The following intervals 
\begin{equation}
\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
 & \cup\{\imposs,\necess\}
\end{aligned}
\end{equation}
are overlapping intervals with length~$1/n$ except for the intervals
with length~$\left(2n\right)^{-1}$ at each end. As shown in Table~\ref{tab:I_n},
for each interval~$[\ell,r]$, we define $\textrm{Int}\left([\ell,r]\right)$,
the non-overlapping interior part of $[\ell,r]$.
\begin{table}
\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their lengths, and
their interiors, where $2\mid k$ means $k$ is even, and $2\nmid k$
means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}

@@

Because $\rho\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
there is always a state consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$.
Moreover, by introducing a notion of distance between two states~$\rho$
and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
the collection of states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
gets closer and closer to $\rho$ with respect to $\left\Vert \cdot\right\Vert $
as the intervals get narrower and narrower.

\begin{thm}[Finite-precision Extension of Gleason's theorem for the
Born QIVPMs]\label{thm:Finite-precision-Gleason}In a Hilbert space
$\Hilb$ of dimension $3$, given any state~$\rho$, if a state~$\rho'\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
then their distance~$\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}

\noindent Given state~$\rho'$ consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
the difference between their Born quantum probabilities on any 1-dimensioal
projector~$\proj{\psi}$ is $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
and must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
by definition.

>>>>

\begin{thm}[Non-extensible of Gleason's theorem to general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
a three-dimensional Hilbert space, there is a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}

@@

In other words, if the measurement intervals are too imprecise, the
results we get might contradict to each other, and exclude any possible
state being consistent with the measurement results. Although we will
not dig into the general framework to avoid this problem here~\citep{HOSTunpublished},
we will solve this problem with a concrete family of intervals and
QIVPMs. Consider the following intervals 
\begin{equation}
\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
 & \cup\{\imposs,\necess\}
\end{aligned}
\end{equation}
which are overlapping intervals with length~$1/n$ except for the
intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
in Table~\ref{tab:I_n}, for each interval~$[\ell,r]$, we define
$\textrm{Int}\left([\ell,r]\right)$, the non-overlapping interior
part of $[\ell,r]$.
\begin{table}
\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their lengths, and
their interiors, where $2\mid k$ means $k$ is even, and $2\nmid k$
means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}

@@

In contrast with the QIVPM defined in Thm.~\ref{thm:Non-extensible-of-Gleason's},
there is always a state consistent with a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
because $\rho\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$.
Moreover, by introducing a notion of distance between two states~$\rho$
and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
the collection of states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower.

\begin{thm}[Finite-precision Extension of Gleason's theorem for the
Born QIVPMs]\label{thm:Finite-precision-Gleason}In a three-dimensional
Hilbert space, given any state~$\rho$, if a state~$\rho'\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
then their distance~$\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}

\noindent Given a state~$\rho'$ consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
we have $\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)$
on any 1-dimensioal projector~$\proj{\psi}$ by Thm.~\ref{thm:Finite-precision-Born}.
Since the maximum length of the intervals in $\mathscr{I}_{n}$ is
$1/n$, the difference between the Born quantum probabilities~$\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$
is bounded by $1/n$.  This implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
by definition.
